---
title: "Solution"
author: "Cobey Weemes"
date: "2022-10-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Team A Stats
```{r}
nonCornerTwoPointAttemptsA <- sum(shots_data$team == 'Team A' & (sqrt((shots_data$x)^2 + (shots_data$y)^2) < 23.75) & shots_data$y > 7.8)
nonCornerTwoPointAttemptsA
```
```{r}
cornerTwoPointAttemptsA <- sum(shots_data$team == 'Team A' & (sqrt((shots_data$x)^2 + (shots_data$y)^2) < 22) & shots_data$y <= 7.8)
cornerTwoPointAttemptsA
```
```{r}
nonCornerTwoPointMakesA <- sum(shots_data$team == 'Team A' & (sqrt((shots_data$x)^2 + (shots_data$y)^2) < 23.75)& shots_data$y > 7.8 & shots_data$fgmade == 1)
nonCornerTwoPointMakesA
```
```{r}
cornerTwoPointMakesA <- sum(shots_data$team == 'Team A' & (sqrt((shots_data$x)^2 + (shots_data$y)^2) < 22)& shots_data$y <= 7.8 & shots_data$fgmade == 1)
cornerTwoPointMakesA
```
```{r}
nonCornerThreePointAttemptsA <- sum(shots_data$team == 'Team A' & (sqrt((shots_data$x)^2 + (shots_data$y)^2) > 23.75) & shots_data$y > 7.8)
nonCornerThreePointAttemptsA
```
```{r}
cornerThreePointAttemptsA <- sum(shots_data$team == 'Team A' & (sqrt((shots_data$x)^2 + (shots_data$y)^2) > 22) & shots_data$y <= 7.8)
cornerThreePointAttemptsA
```

```{r}
nonCornerThreePointMakesA <- sum(shots_data$team == 'Team A' & (sqrt((shots_data$x)^2 + (shots_data$y)^2) > 23.75) & shots_data$y > 7.8 & shots_data$fgmade == 1)
nonCornerThreePointMakesA
```

```{r}
cornerThreePointMakesA <- sum(shots_data$team == 'Team A' & (sqrt((shots_data$x)^2 + (shots_data$y)^2) > 22)& shots_data$y <= 7.8 & shots_data$fgmade == 1)
cornerThreePointMakesA
```

#Shot distributions for two pointers Team A
```{r}
totalA = nonCornerTwoPointAttemptsA + cornerTwoPointAttemptsA + nonCornerThreePointAttemptsA + cornerThreePointAttemptsA
```

#Two point zone
```{r}
shotDistTwoPointTeamA = ((nonCornerTwoPointAttemptsA + cornerTwoPointAttemptsA) / totalA) * 100
shotDistTwoPointTeamA
```

#Three point non corner zone
```{r}
shotDistNonCornerThreePointTeamA = (nonCornerThreePointAttemptsA / totalA) * 100
shotDistNonCornerThreePointTeamA
```

#Three point corner zone
```{r}
shotDistCornerThreePointTeamA = (cornerThreePointAttemptsA / totalA) * 100
shotDistCornerThreePointTeamA
```

#Effective field goal % for every shot
```{r}
(((nonCornerTwoPointMakesA + cornerTwoPointMakesA + nonCornerThreePointMakesA + cornerThreePointMakesA) + ((.5)*(nonCornerThreePointMakesA + cornerThreePointMakesA))) / totalA) * 100
```

#Effective field goal % for two pointers
```{r}
(((nonCornerTwoPointMakesA + cornerTwoPointMakesA) + ((.5)*(0))) / totalA) * 100
```

#Effective field goal % for three pointers non corner
```{r}
(((nonCornerThreePointMakesA) + ((.5)*(nonCornerThreePointMakesA))) / totalA) * 100
```

#Effective field goal % for three pointers corner
```{r}
(((cornerThreePointMakesA) + ((.5)*(cornerThreePointMakesA))) / totalA) * 100
```

#Team B Stats

```{r}
nonCornerTwoPointAttemptsB <- sum(shots_data$team == 'Team B' & (sqrt((shots_data$x)^2 + (shots_data$y)^2) < 23.75) & shots_data$y > 7.8)
nonCornerTwoPointAttemptsB
```
```{r}
cornerTwoPointAttemptsB <- sum(shots_data$team == 'Team B' & (sqrt((shots_data$x)^2 + (shots_data$y)^2) < 22) & shots_data$y <= 7.8)
cornerTwoPointAttemptsB
```
```{r}
nonCornerTwoPointMakesB <- sum(shots_data$team == 'Team B' & (sqrt((shots_data$x)^2 + (shots_data$y)^2) < 23.75)& shots_data$y > 7.8 & shots_data$fgmade == 1)
nonCornerTwoPointMakesB
```
```{r}
cornerTwoPointMakesB <- sum(shots_data$team == 'Team B' & (sqrt((shots_data$x)^2 + (shots_data$y)^2) < 22)& shots_data$y <= 7.8 & shots_data$fgmade == 1)
cornerTwoPointMakesB
```
```{r}
nonCornerThreePointAttemptsB <- sum(shots_data$team == 'Team B' & (sqrt((shots_data$x)^2 + (shots_data$y)^2) > 23.75) & shots_data$y > 7.8)
nonCornerThreePointAttemptsB
```
```{r}
cornerThreePointAttemptsB <- sum(shots_data$team == 'Team B' & (sqrt((shots_data$x)^2 + (shots_data$y)^2) > 22) & shots_data$y <= 7.8)
cornerThreePointAttemptsB
```

```{r}
nonCornerThreePointMakesB <- sum(shots_data$team == 'Team B' & (sqrt((shots_data$x)^2 + (shots_data$y)^2) > 23.75) & shots_data$y > 7.8 & shots_data$fgmade == 1)
nonCornerThreePointMakesB
```

```{r}
cornerThreePointMakesB <- sum(shots_data$team == 'Team B' & (sqrt((shots_data$x)^2 + (shots_data$y)^2) > 22)& shots_data$y <= 7.8 & shots_data$fgmade == 1)
cornerThreePointMakesB
```

#Shot distribution for two pointers Team B
```{r}
totalB = nonCornerTwoPointAttemptsB + cornerTwoPointAttemptsB + nonCornerThreePointAttemptsB + cornerThreePointAttemptsB
totalB
```
#Two point zone
```{r}
shotDistTwoPointTeamB = ((nonCornerTwoPointAttemptsB + cornerTwoPointAttemptsB) / totalB) * 100
shotDistTwoPointTeamB
```

#Three point non corner zone
```{r}
shotDistNonCornerThreePointTeamB = (nonCornerThreePointAttemptsB / totalB) * 100
shotDistNonCornerThreePointTeamB
```

#Three point corner zone
```{r}
shotDistCornerThreePointTeamB = (cornerThreePointAttemptsB / totalB) * 100
shotDistCornerThreePointTeamB
```

#Effective field goal % for every shot
```{r}
(((nonCornerTwoPointMakesB + cornerTwoPointMakesB + nonCornerThreePointMakesB + cornerThreePointMakesB) + ((.5)*(nonCornerThreePointMakesB + cornerThreePointMakesB))) / totalB) * 100
```

#Effective field goal % for two pointers
```{r}
(((nonCornerTwoPointMakesB + cornerTwoPointMakesB) + ((.5)*(0))) / totalB) * 100
```

#Effective field goal % for three pointers non corner
```{r}
(((nonCornerThreePointMakesB) + ((.5)*(nonCornerThreePointMakesB))) / totalB) * 100
```

#Effective field goal % for three pointers corner
```{r}
(((cornerThreePointMakesB) + ((.5)*(cornerThreePointMakesB))) / totalB) * 100
```



```{r}

```

